weight_analyses

### 2022-10-26 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
Minor updates to tables - changed "Site" to "Location" to match Nicole and added Location to survival table

survival_RV <- Cagetype_survival_RV %>%
   mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)
```

@@

survival_DWSC <- Cagetype_survival_DWSC %>%
  mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)
```

EDI table for survival
```{r}
survival_bind <- rbind(survival_DWSC, survival_RV) %>%
  mutate(rate = round(rate,2))
write_csv(survival_bind, here::here("smelt_2019_winterspring", "data_clean", "2019_smeltstudy_survival_data.csv"))
```

>>>>

survival_RV <- Cagetype_survival_RV %>%
   mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Site, Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)
```

@@

survival_DWSC <- Cagetype_survival_DWSC %>%
  mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Site, Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)
```

EDI table for survival
```{r}
survival_bind <- rbind(survival_DWSC, survival_RV) %>%
  mutate(rate = round(rate,2)) %>%
  rename(Location = Site)
write_csv(survival_bind, here::here("smelt_2019_winterspring", "data_clean", "2019_smeltstudy_survival_data.csv"))
```
